\textbf{Supplementary Information for the T-reX Manuscript}

### 2024-03-06 latex_files/main.tex
add sankeys, etc.

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,3p,times,authoryear]{elsarticle}
%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
\documentclass[review,3p,authoryear]{elsarticle}
%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}
\usepackage{lineno}
\usepackage{booktabs}
% ---------------------------------------------------------------------
%             FOR DRAFTING / REVIEW (DELETE BEFORE SUBMISSION)
% ---------------------------------------------------------------------
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[british]{babel}
\usepackage{microtype}
\usepackage[tt=false]{libertine}
\usepackage{xcolor}
\definecolor{blue}{RGB}{33,150,209}
\definecolor{red}{RGB}{255,0,0}
\usepackage{xurl}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{pdfpages}
\usepackage{enumitem}
\usepackage{lineno}
\usepackage{float}
\setlength{\linenumbersep}{5pt}
% Save the old \texttt command
\let\oldtexttt\texttt
% Redefine the \UrlFont to use a smaller typewriter font
\renewcommand{\UrlFont}{\ttfamily\small}
% Redefine the \texttt command to use a smaller font size and allow line breaks
\renewcommand{\texttt}[1]{{\ttfamily\small\nolinkurl{#1}}}

@@

\linenumbers

@@

    \begin{abstract}
        \cbox{Abstract word count: 158, Limit: 150}
        Minimising material consumption and waste generation is the quintessential principle of the `circular economy'.
        Thus, identifying and quantifying waste and material flows are of fundamental importance. Life Cycle Assessment (LCA) is powerful for this end, given its capacity to pinpoint hotspots of environmental impact throughout the life cycle of products and services, those where the implementation of circular principles could be most effective.

        Introducing T-reX, a Python tool extending the `Brightway' LCA ecosystem, allowing facile quantification of user-defined supply-chain demands in current and prospective scenarios. T-reX streamlines database manipulation for LCA practitioners and integrates methods to aggregate and analyse waste and material flows, facilitating rapid hotspot identification.

@@

\section{Methodology}
\label{sec:methodology}
\cbox{Section word count: 800}
\input{methodology.tex}

\section{Results}
\cbox{Section word count: 1400}
\label{sec:results}
\input{results.tex}

@@

\section{Conclusions}
\label{sec:conclusions}
\cbox{Section word count: 250}
We have written the T-reX tool, an extension to the brightway LCA framework that enables the user to calculate the waste and material footprints of a product or service in an LCA database. It explodes the database, identifies upstream waste and material exchanges, edits them, and writes matching custom `pseudo' LCIA methods. These exchanges become pseudo-biosphere flows and thus, the footprint can be calculated as with the existing LCIA methods. The T-reX tool can be easily customised by the user to calculate the footprints of other supply-chain flows such as water, gas, and critical raw materials.

@@

\section*{Supplementary material}
    The supplementary material contains the following:
    \begin{enumerate}
        \item List of waste and material categories
        \item Example output of the T-reX tool
        \item List of identified waste and material exchanges
        \item Code (python script) used for case study
        \item Inventory and methods used in the case study
        \item Complete tabulated results of the case study
        \item Complete visualisations of the case study
    \end{enumerate}

>>>>

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,3p,times,authoryear]{elsarticle}
%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
\documentclass[review,3p,authoryear]{elsarticle}
%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}
\usepackage{booktabs}
% ---------------------------------------------------------------------
%             FOR DRAFTING / REVIEW (DELETE BEFORE SUBMISSION)
% ---------------------------------------------------------------------
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[british]{babel}
\usepackage{microtype}
\usepackage[tt=false]{libertine}
\usepackage{xcolor}
\definecolor{blue}{RGB}{33,150,209}
\definecolor{red}{RGB}{255,0,0}
\usepackage{xurl}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{pdfpages}
\usepackage{enumitem}
\usepackage{lineno}
\usepackage{float}
\setlength{\linenumbersep}{5pt}
% Save the old \texttt command
\let\oldtexttt\texttt
% Redefine the \UrlFont to use a smaller typewriter font
\renewcommand{\UrlFont}{\ttfamily\small}
% Redefine the \texttt command to use a smaller font size and allow line breaks
\renewcommand{\texttt}[1]{{\ttfamily\small\nolinkurl{#1}}}

@@

% \linenumbers

@@

    \begin{abstract}
        \cbox{Abstract word count: 151, Limit: 150}
        Minimising material consumption and waste generation is the quintessential principle of the `circular economy'.
        Thus, identifying and quantifying waste and material flows are of fundamental importance. Life Cycle Assessment (LCA) is powerful for this end, given its capacity to pinpoint hotspots of environmental impact throughout the life cycle of activities, where the implementation of circular principles could be most effective.

        Introducing T-reX, a Python tool extending the brightway ecosystem, allowing facile quantification of user-defined supply-chain demands in current and prospective scenarios. T-reX streamlines database manipulation for LCA practitioners and integrates methods to aggregate and analyse waste and material flows, facilitating rapid hotspot identification.

@@

\section{Methodology}
\label{sec:methodology}
\cbox{Section word count: 1600}
\input{methodology.tex}

\section{Results}
\cbox{Section word count: 1300}
\label{sec:results}
\input{results.tex}

@@

\section{Conclusions}
\label{sec:conclusions}
\cbox{Section word count: 250}
We have created the T-reX tool, an extension to the brightway LCA ecosystem that enables users to calculate the waste and material footprints of a product or service in an LCA database. It explodes the database, identifies upstream waste and material exchanges, edits them, and writes matching custom `pseudo' LCIA methods. These exchanges become pseudo-biosphere flows and thus, the footprint can be calculated as with the existing LCIA methods. The T-reX tool can be easily customised by the user to calculate the footprints of other supply-chain flows such as water, gas, and critical raw materials.

@@

\section*{Supplementary material}
    The supplementary material contains the following:
    \begin{enumerate}
        \item Metadata of the T-reX python package
        \item Details of the modules and user configuration
        \item Description of the computational workflow
        \item Modular flowchart of the T-reX tool
        \item Example of the terminal output of the T-reX tool
        \item Complete tabulated results of the case study
        \item Complete visualisations of the case study
    \end{enumerate}

### 2024-03-06 latex_files/results.tex
add sankeys, etc.

\subsubsection{Temporal and scenario variation in waste and material footprints}\label{sec:results-case_study-total_footprints}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{figures/total_waste.png}
    \caption{Total solid waste footprints for the five Li-ion batteries in the case study from 2020 to 2100 under the SSP2 scenario using the baseline and PkBudg500 RCPs of the REMIND model.}\label{fig:waste_total}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{figures/carbondioxide.png}
    \caption{Carbon dioxide waste (from carbon capture and storage) footprints for the five Li-ion batteries in the case study from 2020 to 2100 under the SSP2 scenario using the baseline and PkBudg500 RCPs of the REMIND model.}\label{fig:carbondioxide}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{figures/phosphate.png}
    \caption{Phosphate material demand footprints for the five Li-ion batteries in the case study from 2020 to 2100 under the SSP2 scenario using the baseline and PkBudg500 RCPs of the REMIND model.}\label{fig:phosphate}
\end{figure}

>>>>

\subsubsection{Sankey visualisation of flows in waste and material inventory footprints}\label{sec:results-case_study-sankey}
\

\autoref{fig:sankey} Sankey diagram of the total solid waste footprint flows for the NMC 811 battery in the case study
\cbox{I won't write about these until I know what figures we want to show. We can explore them in ActivityBrowser and decide.}

\textcolor{red}{[and decide which ones are most interesting (or will fit on a page. The most interesting are the ones that look like the flying spaghetti monster). I would probably make a new sankey (back to coding!), or edit the AB one in inkscape to make it understandable on the page.]}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{figures/T-reX\_NMC811\_WasteTotalSolid.pdf}
    \caption{Sankey diagram of the total solid waste footprint flows for the NMC 811 battery in the case study.}\label{fig:sankey_waste}
\end{figure}

\autoref{fig:sankey_material} shows the Sankey diagram of the chromium inventory demand footprint flows for the LFP battery in the case study.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{figures/T-reX\_NMC811\_WasteTotalSolid.pdf}
    \caption{Sankey diagram of the chromium inventory demand footprint flows for the LFP battery in the case study.}\label{fig:sankey_material}
\end{figure}

\subsubsection{Temporal and scenario variation in waste and material inventory footprints}\label{sec:results-case_study-total_footprints}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{figures/total_waste.png}
    \caption{Total solid waste footprints for the five Li-ion batteries in the case study from 2020 to 2100 under the SSP2 scenario using the baseline and PkBudg500 RCPs of the REMIND model.}\label{fig:waste_total}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{figures/carbondioxide.png}
    \caption{Carbon dioxide waste (from carbon capture and storage) footprints for the five Li-ion batteries in the case study from 2020 to 2100 under the SSP2 scenario using the baseline and PkBudg500 RCPs of the REMIND model.}\label{fig:carbondioxide}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{figures/phosphate.png}
    \caption{Phosphate material demand footprints for the five Li-ion batteries in the case study from 2020 to 2100 under the SSP2 scenario using the baseline and PkBudg500 RCPs of the REMIND model.}\label{fig:phosphate}
\end{figure}
